Comprehensive study of the global phase diagram of the $J$-$K$-$\Gamma$ model on a triangular lattice

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 13:57

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual GS entropy. The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration. In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. G. Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbital coupling, electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases. The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204,10.1146/annurev-conmatphys-033117-053934}, in which the NN Heisenberg interaction is also taken into account. This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits. Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e. bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}. Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included. Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204,Winter_2017,10.1038/s42254-019-0038-2}. Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevB.93.214431,PhysRevB.96.115103}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) \replaced[swang]{Zero-temperature global}{Global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases denoted as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-C phases given by the classical analyses.}
\end{figure*}

@@

In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e. $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.

When we carefully examine the SSF near $\beta=0.5\pi$, we find that the SSF is obviously different from those of the stripe phases. As shown in Fig.~\ref{fig:StructureFactors}(e) for $\alpha=0.3\pi$ and $\beta=0.5\pi$, besides the peaks at the $\tilde{M}$ points, the SSF also shows significant intensities along the boundary of the BZ. In order to clarify whether there is another magnetically ordered phase near $\beta=0.5\pi$, we use the ``basin-hopping" technique again to search for the possible spin order for $\alpha=0.3\pi$ and $\beta=0.5\pi$ on a $12 \times 12$ lattice. The spin configuration is depicted in Fig.~\ref{fig:ModulatedStripe}(a), which exhibits a modulated stripe order. For this modulated stripe order, the spins are FM along a next-nearest-neighbor direction and the spin orientation of the FM chains are modulated along the direction perpendicular to the FM chains to form a structure with a period of six. As illustrated in Fig.~\ref{fig:ModulatedStripe}(b), the SSF of this classical six-chain stripe order shows clear peaks at the $\tilde{K}$ points in addition to those at the $\tilde{M}$ points, which is consistent with the characteristic of the SSF in Fig.~\ref{fig:StructureFactors}(e) calculated by the ED. We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the GS spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c). We find that the spin arrangement is still a modulated stripe order, although the spin orientations are also modulated along the FM chains in addition to a larger modulated period perpendicular to the chains. Thus, we unveil an unnoticed phase in the region between the stipe-A and stripe-C phase and term it the modulated stripe order phase.

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. The SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have FM orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform an analysis based on the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). However, according to our ED calculations, for the quantum model, quantum fluctuations select the FM ordered states as the GS out of the degenerate manifolds of classical states. This selection of states among the degenerate classical GSs is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical GS configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) stripe-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL. The green dashed lines mark the first BZ of the triangular lattice. (i) Characteristic wave vectors for the \replaced[swang]{FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)}{FM and stripe} phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

@@

@@

\begin{acknowledgments}
This work was supported by the National Natural Science Foundation of China (Grants No. 11674158, No. 11774152\replaced[swang]{, No. 11774300 and No. 12004191}{ and No. 11774300})\replaced[swang]{,}{ and} National Key Projects for Research and Development of China (Grant No. 2016YFA0300401) \added[swang]{and Natural Science Foundation of Jiangsu Province, China (Grant No. BK20200738)}.
\end{acknowledgments}

@@

\added[swang]{
    \section{\label{apx:SizeEffect}The effects of system size on the phase boundaries}
    To study the effects of system size on the zero-temperature quantum phase diagram, we carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the cluster as well as the periodic boundary condition. This cluster is compatible with most of the magnetic orders, such as FM, stripe, 120$^\circ$ N\'{e}el, dual N\'{e}el and modulated stripe shown in Fig.~\ref{fig:ModulatedStripe}(a).

    In Fig.~\ref{fig:SecondDerivatives26}(a)-(c), the $\alpha$ parameter is fixed to $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively. In Fig.~\ref{fig:SecondDerivatives26}(d)-(f), the $\beta$ parameter is fixed to 0, $0.5\pi$ and $1.5\pi$, respectively. The singularities in Fig.~\ref{fig:SecondDerivatives26}(a)-(f) are consistent with the results of the $4 \times 6$ cluster shown in Fig.~\ref{fig:SecondDerivatives46}(a)-(f) even though the positions of the phase boundaries are slightly shifted. It is worth to note that, in Fig.~\ref{fig:SecondDerivatives26}(b) the $\beta$ parameter is fixed to $0.2\pi$ while in Fig.~\ref{fig:SecondDerivatives46}(b) $\beta = 0.3\pi$. The reason to take different $\beta$ parameter is that for $2 \times 6$ cluster the region of the 120$^\circ$ N\'eel phase would extend to larger area. If we continue take $\beta = 0.3\pi$, the singularities in -$\partial^2E_0 / \partial \alpha^2$ would not correspond to the peaks shown in Fig.~\ref{fig:SecondDerivatives46}(b). In a word, different system size only has effects on the positions of the phase boundaries but not these quantum phases.

    \begin{figure}
        \centering
        \includegraphics[width=\columnwidth]{fig/SecondDerivatives26.pdf}
        \includegraphics[width=\columnwidth]{fig/Cluster26.pdf}
        \added[swang]{
            \caption{\label{fig:SecondDerivatives26} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ along the same paths shown in Fig.~\ref{fig:SecondDerivatives46}. The blue lines are the GS energies and the red lines are the second derivatives. In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.3\pi$ and $0.75\pi$, respectively. In (d)-(f), $\beta$ is fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively. (g) The $2 \times 6$ cluster as well as the periodic boundary condition that is used to perform the ED calculations.}
        }
    \end{figure}
}

>>>>

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and give raise to a residual GS entropy. The spin-$1/2$ Kitaev model~\cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless QSL states supporting fractionalized excitations, is a celebrated example of a model with exchange frustration. In this model, the spins subject to the Kitaev interactions consisting of nearest neighbor Ising-type interactions, with the quantization axis depending on the spatial orientation of an exchange bond. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search for a solid-state realization of the Kitaev model. G. Khaliullin \emph{et al.,}~\cite{Khaliullin2005,PhysRevLett.102.017205} proposed that this highly anisotropic Kitaev interaction can be realized in 4d/5d systems with a low spin state of $d^5$ configuration, such as iridates A$_2$IrO$_3$ (A = Na, Li). In these systems, the bond-directional interactions originate from the joint effects of strong spin-orbital coupling, electron interactions, $d^5$ configuration and 90$^\circ$ bond geometry formed by edge sharing octahedra. However, in real materials, other types of interaction besides the Kitaev coupling are present, and these interactions may induce other interesting ordered and disordered phases. The simplest extension of the pure Kitaev model is the Heisenberg-Kitaev (HK) model~\cite{PhysRevLett.105.027204,10.1146/annurev-conmatphys-033117-053934}, in which the NN Heisenberg interaction is also taken into account. This model has been extensively studied by various numerical methods~\cite{PhysRevLett.110.097204,PhysRevB.83.245104,PhysRevB.84.100406,PhysRevB.90.195102,PhysRevLett.119.157203}, which reveal the presence of four magnetically ordered phases with collinear spin patterns of ferromagnetic (FM), AFM, stripe, and zigzag types, besides extended spin-liquid phases near the Kitaev limits. Considering the most idealized crystal structure, another interaction beyond the HK model also must be included, i.e., bond dependent symmetric off-diagonal exchange, which is called the $\Gamma$ interaction~\cite{PhysRevLett.112.077204,PhysRevB.93.214431,PhysRevB.96.115103}. Thus, the generic NN exchange Hamiltonian for the undistorted hexagonal compounds is the $J$-$K$-$\Gamma$ model, where the Heisenberg ($J$), Kitaev ($K$) and $\Gamma$ interactions are all included. Finite $\Gamma$ further enriches the phase diagram by adding non-collinear and incommensurate spiral phases~\cite{PhysRevLett.112.077204,Winter_2017,10.1038/s42254-019-0038-2}. Moreover, in real materials, such as A$_2$IrO$_3$ and $\alpha$-RuCl$_{3}$, the dominant interactions are the $\Gamma$ and FM Kitaev terms which originate from both direct $d$-$d$ and anion mediated $d$-$p$ electron transfer, while the Heisenberg term has the smallest strength since it predominantly originates from the weak direct $d$-$d$ electron transfer~\cite{PhysRevB.93.214431,PhysRevB.96.115103}.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) \added[swang]{Zero-temperature global} phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases denoted as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-C phases given by the classical analyses.}
\end{figure*}

@@

In Fig.~\ref{fig:StructureFactors}(b) and (c), we show the SSFs for two typical points in the stripe-A phase, i.e., $\alpha=0.3\pi$, $\beta=0.75\pi$ and $\alpha=0.75\pi$, $\beta=0.25\pi$ in the $\Gamma>0$ and $\Gamma<0$ regions, respectively. Both of the SSFs show obvious peaks at the $\tilde{M}$ points, which is a typical characteristic of the stripe order as shown in Fig.~\ref{fig:StructureFactors}(i). Thus, this further confirms that the stripe-A phase extents to a large region in the phase diagram. In Fig.~\ref{fig:StructureFactors}(d), we illustrate the SSF for $\alpha=0.3\pi$, $\beta=0$ for one of the new phase that does not exist in the HK limit, which also shows distinct peaks at the $\tilde{M}$ points, so the phase containing this point is also a stripe phase and we denote it the stripe-C phase in the phase diagram.
\added[swang]{The difference between stripe-A, stripe-B and stripe-C lies in that they have different moment directions, which we will discuss in detail later.}

When we carefully examine the SSF near $\beta=0.5\pi$, we find that the SSF is obviously different from those of the stripe phases. As shown in Fig.~\ref{fig:StructureFactors}(e) for $\alpha=0.3\pi$ and $\beta=0.5\pi$, besides the peaks at the $\tilde{M}$ points, the SSF also shows significant intensities along the boundary of the BZ. In order to clarify whether there is another magnetically ordered phase near $\beta=0.5\pi$, we use the ``basin-hopping" technique again to search for the possible spin order for $\alpha=0.3\pi$ and $\beta=0.5\pi$ on a $12 \times 12$ lattice. The spin configuration is depicted in Fig.~\ref{fig:ModulatedStripe}(a), which exhibits a modulated stripe order. For this modulated stripe order, the spins are FM along a next-nearest-neighbor direction and the spin orientation of the FM chains are modulated along the direction perpendicular to the FM chains to form a structure with a period of six. As illustrated in Fig.~\ref{fig:ModulatedStripe}(b), the SSF of this classical six-chain stripe order shows clear peaks at the $\tilde{K}$ points in addition to those at the $\tilde{M}$ points, which is consistent with the characteristic of the SSF in Fig.~\ref{fig:StructureFactors}(e) calculated by the ED. We further perform a classical Monte Carlo simulations (see Sec.~\ref{subsec:MethodMC}) on a $24 \times24$ lattice to check the stability of the modulated stripe order in the large-size systems, and the GS spin configuration is shown in Fig.~\ref{fig:ModulatedStripe}(c). We find that the spin arrangement is still a modulated stripe order, although the spin orientations are also modulated along the FM chains in addition to a larger modulated period perpendicular to the chains. Thus, we unveil an unnoticed phase in the region between the stripe-A and stripe-C phase and term it the modulated stripe order phase.

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. The SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have FM orders and they are denoted with FM-B and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform an analysis based on the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, there are also several noncollinear magnetic orders energetically degenerate with the FM state (see Appendix~\ref{apx:DegeneratedStates} for details). However, according to our ED calculations, for the quantum model, quantum fluctuations select the FM ordered states as the GS out of the degenerate manifolds of classical states. This selection of states among the degenerate classical GSs is the so called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical GS configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SSFs from the ED calculations for representative interaction parameters in different phases: (a) stripe-B, (b) and (c) stripe-A, (d) stripe-C, (e) modulated stripe, (f) FM-B, (g) FM-C, (h) QSL. The green dashed lines mark the first BZ of the triangular lattice. (i) Characteristic wave vectors for the \added[swang]{FM (blue circle), stripe (orange square), 120$^\circ$ N\'{e}el (red up-triangle) and dual N\'{e}el (purple down-triangle)} phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

@@

\added[swang]{The most commonly used physcial quantity to distinguish different quantum phases is the order parameter. The order parameter of FM, stripe, 120$^\circ$ N\'eel and dual N\'eel states can be defined as $\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector of these magnetically ordered states. However since the cluster ground state does not spontaneously break the symmetry and corresponds to a superposition of all possible degenerate orderings, the calculated ground state average may give no useful information.}

@@

\begin{acknowledgments}
This work was supported by the National Natural Science Foundation of China (Grants No. 11674158, No. 11774152, No. 11774300, \added[swang]{No. 12004191 and No. 12074175}, National Key Projects for Research and Development of China (Grant No. 2016YFA0300401) \added[swang]{and Natural Science Foundation of Jiangsu Province, China (Grant No. BK20200738)}.
\end{acknowledgments}

@@

\added[swang]{
\section{\label{apx:SizeEffect}The effects of system size on the phase boundaries}
To study the effects of system size on the zero-temperature quantum phase diagram, we also carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the shape of the cluster as well as the form of the boundary condition. This cluster and the boundary condition are compatible with most of the magnetic orders, such as FM, stripe, 120$^\circ$ N\'{e}el, dual N\'{e}el and six-chain modulated stripe shown in Fig.~\ref{fig:ModulatedStripe}(a).

In Fig.~\ref{fig:SecondDerivatives26}(a)-(c), the $\alpha$ parameter is fixed to $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively. In Fig.~\ref{fig:SecondDerivatives26}(d)-(f), the $\beta$ parameter is fixed to 0, $0.5\pi$ and $1.5\pi$, respectively. The singularities in Fig.~\ref{fig:SecondDerivatives26}(a)-(f) are consistent with the results of the $4 \times 6$ cluster shown in Fig.~\ref{fig:SecondDerivatives46}(a)-(f) even though the positions of the phase boundaries are slightly shifted. It is worth to note that, in Fig.~\ref{fig:SecondDerivatives26}(b) the $\beta$ parameter is fixed to $0.2\pi$ while in Fig.~\ref{fig:SecondDerivatives46}(b) $\beta = 0.3\pi$, since the region of the 120$^\circ$ N\'eel phase extends to a larger area for the $2 \times 6$ cluster, which leads to that $\beta = 0.3\pi$ is still in the 120$^\circ$ N\'eel phase. Thus, in comparison with the results for the $4 \times 6$ cluster, we find that different system sizes do not change the phase diagram qualitatively and only affect the locations of the phase boundaries.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/SecondDerivatives26.pdf}
  \includegraphics[width=\columnwidth]{fig/Cluster26.pdf}
  \added[swang]{
  \caption{\label{fig:SecondDerivatives26} (Color online) GS energies and their second derivatives versus $\alpha$ or $\beta$ along the same paths shown in Fig.~\ref{fig:SecondDerivatives46}. The blue lines are the GS energies and the red lines are the second derivatives. In (a)-(c) $\alpha$ is fixed to $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively. In (d)-(f), $\beta$ is fixed to $0$, $0.5\pi$ and $1.5\pi$, respectively. (g) The $2 \times 6$ cluster as well as the periodic boundary condition that is used to perform the ED calculations.}
  }
\end{figure}
}
